### 2025-06-12 question_papers/aima203_first_in_sem.tex
question paper

\question Find a root of $x^3-4x-9=0$, using bisection method, with absolute error less than $10^2$. [4]

\question Describe error due to truncation. Find a root of \(f(x)=xe^x-1=0\), correct to \(2\) decimal places. [1+3]
\end{questions}

\vspace{3cm}
\begin{center}
 {\bfseries  { Kathmandu University}} \\[-1mm]
 First In-Semester Exam-2025\\[-2mm]
 {\small \textbf{Department of Artificial Intelligence, Panchkhal}}
\end{center}
\begin{minipage}{0.70\linewidth}
  \small
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 1mm
\rule{\textwidth}{1pt}

@@

\question Find a root of $x^3-4x-9=0$, using bisection method, with absolute error less than $10^2$. [4]

\question Describe error due to truncation. Find a root of \(f(x)=xe^x-1=0\), correct to \(2\) decimal places. [1+3]
\end{questions}

@@

\vspace{4cm}
\begin{questions}
\question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    25  & 24 \\
    66 & 78 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[2mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]
  \vspace{12cm}

 \question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    25  & 24 \\
    66 & 78 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[1mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]

>>>>

\question Write the rate of convergence of Newton Raphson's method. Find a root of \(f(x)=xe^x-1=0\), correct to \(2\) decimal places. [1+3]

\question Find a real root of the equations $y^2-5y+4=0$ and $3yx^2-10x+7=0$ correct to 3 decimal places, using the method of iteration. [4]

\end{questions}

\vspace{4cm}
\begin{center}
 {\bfseries  {Kathmandu University}} \\[-1mm]
 First In-Semester Exam-2025\\[-2mm]
 {\small \textbf{Department of Artificial Intelligence, Panchkhal}}
\end{center}
\begin{minipage}{0.70\linewidth}
  \small
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 1mm
\rule{\textwidth}{1pt}

@@

\question Write the rate of convergence of Newton Raphson's method. Find a root of \(f(x)=xe^x-1=0\), correct to \(2\) decimal places. [1+3]

\question Find a real root of the equations $y^2-5y+4=0$ and $3yx^2-10x+7=0$ correct to 3 decimal places, using the method of iteration. [4]

\end{questions}

@@

  \vspace{4cm}

  \begin{questions}
      \setcounter{question}{3}
\question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    5  & 4 \\
    6 & 8 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[2mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]

 \begin{center}
    \bfseries OR
  \end{center}
  Using Newton's Interpolation formula estimate : $y(10)$ from \\
  $(1,24), \;\;\; (3,120),\;\;\; (5,366), \;\;\; (7,720)$

  \vspace{9cm}
  \setcounter{question}{3}
 \question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    5  & 4 \\
    6 & 8 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[1mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]
  \begin{center}
    \bfseries OR
  \end{center}
  Using Newton's Interpolation formula estimate : $y(10)$ from \\
  $(1,24), \;\;\; (3,120),\;\;\; (5,366), \;\;\; (7,720)$

### 2025-06-12 question_papers/aima203_mcq_first_in_sem.tex
interpolation
question paper

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Roll No: \hspace{5.5cm} Marks Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
  \question Give an example of an approximate value: \rule{8cm}{0.15mm}.

  \question Write the number of significant digits in 20300.00  \rule{5cm}{0.15mm}.

  \question Write the precision of 45.203 \rule{5cm}{0.15mm}.

  \question Write the accuracy of 7953.2300 \rule{5cm}{0.15mm}.

\end{questions}

>>>>

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Name: \hspace{5cm}  Roll No: \hspace{3cm} Marks-Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}

\question Write the number of significant digits in 20300.00  \rule{5cm}{0.15mm}.
  \vspace{2mm}

  \question Write the precision and accuracy of 45.2030  \rule{5cm}{0.15mm}.

  \question Find the upper limit error in rounding a number to $4$ decimal places.\rule{4cm}{0.15mm}.

    \question What is the maximum number of positive real roots of $x^5-x^4+3x^3-x^2-x+2$? \rule{7cm}{0.15mm}.

    \question Which error: Truncation error or rounding off error in Newton Raphson's method? \rule{5cm}{0.15mm}.

    \question Which one converges faster bisection method or secant method? \rule{5cm}{0.15mm}.

    \question Write the disadvantage of ``Lagrange's Interpolation method'': \rule{5cm}{0.15mm} \\[1mm]
      \rule{10cm}{0.15mm}.

    \question Write the advantage of ``Secant method over Newton Rapshon's method'': \\[1mm]
      \rule{12cm}{0.15mm}.

    \question Write the formula for $\Delta y_1$ and $\nabla y_1$: \rule{7cm}{0.15mm}.

    \question What is the difference of interpolation and extrapolation. \rule{5cm}{0.15mm} \\[1mm]
      \rule{12cm}{0.15mm}.

 \question Calculate the number of steps taken by Bisection method to get the accuracy less than $10^{-3}$.\rule{8cm}{0.15mm}.
\end{questions}
